\textbf{International Transport costs:\\New Findings from modeling additive costs}\\Online Appendix (Not for Publication)

### 2021-11-23 redaction/JEGeo/revision_JEGeo/referees/answers/Answer_referee2.tex

\textbf{Our answer:} We devoted a lot of thought to this point, which directly echoed a similar concern by the other referee. The latter writes: ``\emph{Does this observation revise our understanding of say the gains from trade? Does it shed new light on a puzzle many people are thinking about? [One] suggestion is to dig deeper into the relative rate at which additive and multiplicative transport costs have declined over time.}
''

All in all, your suggestion and the other referee's one pointed toward two possible directions for the ``Big Picture'' implications of our exercise: either exploring the compositional country-product dynamics underlying of our results, or focusing on the welfare implications. Both paths were undeniably worth exploring, but could not be followed in a single paper. Therefore, we decided to focus on the second path, i.e. to  offer insights on the welfare implications of our results. In this regard, the new Section 5 ``The role of additive cost: Theoretical insights'' is devoted to a theory-based analysis of the changes to welfare gains implied by the relative variations of additive and multiplicative transport costs over our period of analysis.

Our choice to dig into the welfare implications of our results has two main motivations. Firstly, even if ``\emph{the fact that transport costs are both specific and ad-valorem is well known}'', some recent literature still debates the practical importance of additive costs - for example, \cite{Lashkaripour_JIE2020} recently finds (though in a different theoretical setting) support for the ad-valorem trade cost assumption, i.e, ad-valorem accounting for almost all trade costs. Secondly, the implications of additive costs have not been fully exhausted in \citet{Irrazabal_2015}, \cite{Hornok-et-al-RES-2015, Hornok-et-al-JIE-2015}, \cite{Alessandria-et-al-AER-2010} or \citet{sorensen2014}. \cite{Kropf-Saure-JIE-2016} estimate the size and shape of per-shipment costs based on Swiss data. \cite{Alessandria-et-al-AER-2010} and \cite{Hornok-et-al-RES-2015} point out the role of per-shipment costs in generating ``lumpiness'' in international trade transactions. \cite{Hornok-et-al-JIE-2015} focus on administrative costs incurring with every shipment (i.e., additive by nature), and draw welfare conclusions regarding the variations of these costs. We complement these various outcome by providing a long-run characterization of both additive and multiplicative component of transports costs. Based on these empirical results, we investigate the welfare consequences of the reduction in international transport costs observed over 1974-2019. In this regard, we shed light on the welfare variations induced by the ``hyper-globalization'' period, as well as the disproportionate part of additive transport costs in determining those welfare variations.\smallskip

To this aim, we introduce additive costs in the canonical \citet{melitz} model. The inclusion of additive costs in a \citet{melitz} setting has already been performed in \citet{sorensen2014} and \citet{Irrazabal_2015}. However, \citet{sorensen2014} exclusively performs a theoretical analysis, without any quantitative exercise. In addition to a partial equilibrium extension of \citet{melitz}, \citet{Irrazabal_2015} do perform a quantitative simulation to assess the welfare variations induced by the reduction of additive costs (vs ad-valorem costs). For this, they rely on a calibration for transport costs based on a single-year estimation (for the year 2004), from which they depart by assuming an ad-hoc hypothetical reduction of trade costs. In contrast, our own exercise relies on a several decades of US data, allowing us to highlight the welfare alterations induced over time by the relative dynamics of additive and multiplicative costs, based on the values actually observed in the data over the period 1974-2019, in all their dimensions (additive and ad-valorem).\smallskip

More precisely, we use the estimates underlying results reported in Section 3 concerning multiplicative and additive costs, to implement several comparative statics exercises to investigate the different welfare consequences of alterations to multiplicative and additive costs. In addition, we also assess how the latter results are distorted by changes in sunk costs of exports, $f_{x}$. To that end, we adjust the share of exporting firms in the US. Based on \citet{BEJK-AER-03, Lincoln_McCallum2018}. In our preferred exercise, we quantify the welfare gains that derive from the reduction in variable transport costs as documented in Section 3, relying on a combined reduction in each additive/ad-valorem component in a context of fixed export cost reduction. We compare this with the case where the reduction of total transport costs  is solely attributed to a decrease in ad-valorem costs.

Table 5 in Section 5 of the paper reports the results of these various comparative statics exercises for Air and Vessel transport modes. Specifically, we report the welfare effect of change in total transport costs decomposed in its two dimensions (additive and ad-valorem),both in absolute and in relative terms. We have two major insights. First, using the reduction of transport costs in vessel (air),  welfare gains are around 50\% (14\%) higher when this reduction is achieved through the estimated reduction in additive and ad-valorem costs. Second, the decrease in export sunk costs (i.e., increase in the share of exporting firms) proportionally amplifies the gains from decreasing variable costs, with again an additional premium coming from the decrease of additive costs.

Overall, these results add a substantial contribution to the paper : We are able to provide a quantitative assessment of the welfare gains induced by the decrease in both types (additive and multiplicative) of costs over a 45-year period, and to highlight the respective part of each component in the determination of these gains.
%Note also that not only the inclusion of additive costs in the underlying framework generates large welfare differences, but also that the latter are probably a lower bound of the welfare variations induced by changes in additive \emph{trade} costs, larger than the sole transport costs.

@@

\begin{equation}
p_{ikt}= \sum_i \sum_t \alpha_{it}^\tau \mathbbm{1}_{it}\widetilde{p}_{ikt} +  \sum_k \sum_t \alpha_{kt}^\tau \mathbbm{1}_{kt}\widetilde{p}_{ikt} + \sum_i \sum_t \alpha_{it}^t \mathbbm{1}_{it} + \sum_k \sum_t \alpha_{it}^t\mathbbm{1}_{kt} \label{eq:ref2}
\end{equation}

\textbf{Our answer:} As highlighted by the referee, our estimated equation imposes to use non-linear estimation methods, such as Non-Linear Least Squares. We agree that resorting on a linear form as the one suggested by the referee would substantially alleviate the computational burden. It would have some drawbacks.

First, it can be noticed that the equation suggested by the referee does not stand in accordance with the assumption we borrow from \cite{Irrazabal_2015}, that ad-valorem costs is decomposed in its two country/sector dimensions multiplicatively (i.e. approximating $\tau_{is(k)}$ by the product $\tau_i\times \tau_{s(k)}$.

However, even with another formulation, such as the equations (\ref{eq:ref2_basis}) and (\ref{eq:ref2}) suggested by the referee, we would still be constrained to resort to non-linear estimators. This is due to the restrictions imposed \textit{ex-ante} on parameters, i.e. $\tau \geq 1$ and $t\geq 0$, the latter meaning simply we constrain both types of transport costs to be non-negative, as by construction we cannot have $p_{ikt} < \widetilde{p}_{ikt}$. Without these restrictions, standard linear, least squares estimates deliver aberrant values with mediocre quality-of-fit. Taking into account $p_{ikt} < \widetilde{p}_{ikt}$ also implies that the error term should be always positive, which we ensure by specifying the error term such that:

@@

\begin{equation*}
\frac{p_{ik}}{\widetilde{p}_{ik}}-1 =\left(\tau_{i}\times \tau_{k} -1+\frac{t_{i} + t_{k}}{\widetilde{p}_{ik}} \right)\times \exp(\epsilon_{ik})
\end{equation*}
\noindent where $\epsilon_{ik}$ follows a normal law centered on 0.

This specification obviously requires a non-linear estimation. We did our best to make the point clearer in the revised version (see p.8). We also devote more time to the robustness of the empirical specification. On top of the robustness to the separability assumption (already in the submitted version), we also assess the robustness to the degree of aggregation and endogeneity (Section 3.4). We hope that this new version now convinces you that our estimation strategy is both relevant and robust.

### 2021-11-23 redaction/JEGeo/revision_JEGeo/referees/answers/general_answer_editor_revision.tex

\bigskip
\bigskip

\hfill Paris, \today

\bigskip
\noindent Dear Pr. Kerr, dear Bill, \\
\\
\noindent \noindent We would like to thank you for the opportunity to resubmit our paper, and for your patience in waiting the outcome. We are very grateful for the deadline extensions you kindly granted us. Obviously, the health crisis and the various consecutive lockdowns made the access to our offices difficult in several occurrences. \medskip

However, the major source of delays lies in our attempts to obtain additional data to accommodate a very important concern by Referee \#1 (see below). We ordered this new data from the Census Bureau at the end of December 2019. However, some of the years we requested (2000 and 2001, as well as years before 1998) are not on their servers: they are back at their office which they have not been able to access since last spring apparently, due to the current health situation. Since then, the situation has never evolved, and we are still currently waiting for these missing years. We can of course make available all our e-mail exchanges with Jeremy Sanchez, our contact at the Census Bureau. Until very recently, Mr. Sanchez did not gave us any clear “yes or no” answer to our requests concerning a possible return in his DC office (closed because of the CoViD 19 restrictions), which would have allowed the delivery of the data. In his last e-mail, he confirmed that access to the additional data was impossible.\medskip

Considering the lack of credible perspective to access this additional data in a sufficiently close/foreseeable future, we completed the revision with the following data: a full dataset at the SITC5 level, completed with systematic robustness checks (see the list at the end of this e-mail) based on a HS10 dataset over the 2005-2019 period. These new estimates do not provide any substantial change to our benchmark estimates, and it seems reasonable to consider that additional checks including years from the 1980s and the 1990s would not dramatically change this outcome. \medskip

### 2021-11-23 redaction/JEGeo/revision_JEGeo/referees/answers/general_answer_editor_revision.tex

However, the major source of delays lies in our attempts to obtain additional data to accommodate a very important concern by Referee \#1 (see below). We ordered this new data from the Census Bureau at the end of December 2019. However, some of the years we requested (2000 and 2001, as well as years before 1998) are not on their servers: they are back at their office which they have not been able to access since last spring apparently, due to the current health situation. Since then, the situation has never evolved, and we are still currently waiting for these missing years. We can of course make available all our e-mail exchanges with Jeremy Sanchez, our contact at the Census Bureau. Until very recently, Mr. Sanchez did not gave us any clear “yes or no” answer to our requests concerning a possible return in his DC office (closed because of the CoViD 19 restrictions), which would have allowed the delivery of the data. In his last e-mail, he confirmed that access to the additional data was impossible.\medskip

Considering the lack of credible perspective to access this additional data in a sufficiently close/foreseeable future, we completed the revision with the following data: a full dataset at the SITC5 level, completed with systematic robustness checks (see the list at the end of this e-mail) based on a HS10 dataset over the 2005-2019 period. These new estimates do not provide any substantial change to our benchmark estimates, and it seems reasonable to consider that additional checks including years from the 1980s and the 1990s would not dramatically change this outcome. \medskip

To get now more precisely to the revisions undertaken, we thank the referees for their various comments which led to substantial improvements of the paper. We enclose detailed answers to the referees. Below we detail how we handled two major points raised by both referees, before listing the other major changes brought to the paper.

\section{Two Common Concerns: Estimation Method and Big Picture}
Both referees questioned (i) our empirical methodology, especially our choice of a non-linear estimator and (ii) the lack of a ``big picture'' in the paper, i.e. of a deeper analysis of the implications of our results. Below we detail how we answered their concerns:\medskip

\subsection{Estimation Method}
Both referees challenged our choice of a non-linear estimator, suggesting alternative functional forms that could be estimated with standard linear estimators. We do acknowledge that the initial version of the paper did not make a clear enough case for the non-linear estimator. We now explain in details, both in the papers and in our answers to referees, the reasons why a non-linear estimator is unavoidable in our case. This is due to the restrictions imposed \textit{ex-ante} on parameters, i.e. $\tau \geq 1$ and $t\geq 0$. This restriction is there because we know that both types of transport costs are positive and we do not want to neglect that information. By construction we cannot have $p_{ikt} < \widetilde{p}_{ikt}$. Without these restrictions, standard linear, least squares estimates deliver aberrant values with mediocre quality-of-fit. Taking into account this constraint necessarily brings up a functional requiring a non-linear estimation. We did our best to make the point clearer in the revised version (see p.8). \medskip

@@

That said, resorting to non-linear estimations requires some assumptions due to the computational burden. The revised version devotes much more space to explicit tests of robustness of the empirical specification. On top of the robustness to the separability assumption (already in the initially submitted version), we also assess the robustness to the degree of data aggregation and endogeneity (Section 3.3) - see the list of modifications in section 2 from this letter. \medskip

In this regard, we also point in our answers that implementing the methodology suggested by Referee 1 would imply non-negligible costs. Firstly, this would leave us much less data to exploit, partly  because of the already mentioned CoViD issues - we would lose half of the years in the sample. Secondly, we show in details in our response that our method yields a more precise estimation of transport costs than the referee's method. \medskip

\subsection{Big Picture}
Both referees asked us to shed light on the implications of additive costs (the ``Big Picture''). The revised version answers this concern in two points. \medskip

First, we maintain the analysis of the transport costs time trends (previously [Section 3], now Section 4); but we made our best to make this section easier to read, leaving the technical aspects in the Appendix (Section C). As such, we hope that the main message of this Section is easier to understand. \medskip

Second, and probably more importantly, we now emphasize the ``Big Picture'' implications of additive costs on theoretical grounds. Both referees suggested various, interesting paths to explore. Obviously, all of them could not be handled in a single paper. We have decided to focus on the welfare implications of our results.  Through the lens of the Melitz's (2003) model amended to integrate additive costs, we analyze the welfare gains that derive from the reduction in international transport costs that we have estimated (in Section 3 of the revised version), to quantify the extra welfare gains attributable to the reduction of the additive component. This analysis is conducted in a new Section 5. We emphasize that the theoretical implications of additive costs have not been fully exhausted in Irarrazabal et al. (2015), Hornok and Koren (2015a,b), Alessandria et al. (2010), or Sorensen (2014). Specifically, we use our empirical results to investigate the welfare consequences of the reduction in international transport costs observed over 1974-2019, contrasting two cases: when this reduction is achieved through a combined reduction in the ad-valorem and the additive components (as quantified by our empirical model) or solely through the ad-valorem cost (as modelled in standard New Trade theoretical approaches). To the best of our knowledge, this is the first time that such an assessment is preformed based on long-time, detailed trade data.
\medskip

Overall, we believe these results add a substantial contribution to the paper : we are able to provide a quantitative assessment of the welfare gains induced by the decrease in both types (additive and multiplicative) of costs over a 45-year period, and to highlight the respective part of each component in the determination of these gains. %Note also that not only the inclusion of additive costs in the underlying framework generates large welfare differences, but also that the latter are probably a lower bound of the welfare variations induced by changes in additive \emph{trade} costs, larger than the sole transport costs.

@@

\section{List of major revisions in the new version.}

Below we list the main other revisions implemented to answer referees' concerns:

\begin{enumerate}

\item \emph{Endogeneity issues}: Section 3.3.2 and Appendix B.3 provides detailed developments addressing concerns expressed by Referee 1 concerning potential endogeneity in our estimates. Relying on instrumental variables suggested by Referee 1, we provide first- and second-stage estimates, based on both at the 5-digit-product level and the more disaggregated HS10 level for sensitivity checks. Figure 4 (page 17 \textbf{À vérifier xxxx} in the paper reports our benchmark estimates by transport mode, together with their instrumented counterpart. In all cases, these estimates are very similar. This suggests that our benchmark estimates do not suffer any substantial biases arising from endogeneity concerns.

\item \emph{Aggregation issues}: Referee 1 pointed `` \emph{The original annual Census data reports trade at the origin country-HS10 product-district level of aggregation, whereas the authors are aggregating up the data even further to the origin country-HS5 industry-year level. Such an aggregation comes with strong implicit assumptions and sacrifices a lot of useful variation in the data}.'' Firstly, note these data are available only from 1989, whereas our full sample starts in 1974. Secondly, as already mentioned at the beginning of this letter, it was only possible to get access to the years 1997-1999 and 2001-2019, due to the COVID situation. Considering the importance of having a long time span for our empirical exercise, especially in the context of the welfare analysis, we decided to stick to our initial 5-digit database, and to provide systematic robustness estimates based on the HS10 data available. These results are now reported in section 3.3.3 in the revised version. In particular, Table 3 and Figure ) show the results are similar when using 10-digit product sand 5-digit products \textbf{XXX TO BE CONFIRMED XXX}

\item \emph{Calculation of unit prices}: Referee 1 is concerned by the fact that we calculate unit price as Value/Weight, instead of Value/Quantity. We explain in details in our answer and the online appendix why we decided against a switch from per-kg price to per-unit prices. First, there are data availability issues. Second, the estimation is even more computationaly intensive and third, we believe that the study of per-kg prices adds relevant information to the study of international transport costs, both because actual shipping costs are expressed in a per-weight/volume basis and because it allows us to integrate a larger share of trade in our analysis.

@@

\end{enumerate}

Altogether, we believe that the paper is much clearer and easier to read. The robustness exercises included in the main text focus on the elements that were the most problematic to the referees. Its relevance to big picture debates is more obvious. We hope that you will be pleased by the outcome, and we apology again for the delay.

### 2021-11-23 redaction/JEGeo/revision_JEGeo/referees/answers/Answer_referee2.tex

\title{\textsc{International Transport costs:\\New Findings from modeling additive costs} \\
Answer to Referee 2}

\author{Guillaume \textsc{Daudin}\thanks{%
Université Paris-Dauphine, PSL University, CNRS, 8007, IRD, 260, LEDa, DIAL, 75016, Paris, France ; email: \url{guillaume.daudin@dauphine.psl.eu}}  \qquad J\'{e}r\^{o}me \textsc{H\'{e}ricourt} \thanks{Universit\'{e} de Lille - LEM-CNRS UMR 9221, France \& CEPII, France; email: \url{jerome.hericourt@univ-lille.fr}}\qquad Lise \textsc{Patureau}\thanks{Corresponding author.
University Paris-Dauphine \& PSL University, LEDa, 75016 Paris, France;  email: \url{lise.patureau@dauphine.psl.eu} } }

\date{November 2021}
 \maketitle
\bigskip

We would like to thank you for your insightful comments. They led us to introduce some
significant changes to the paper that we hope address your concerns. We first give you an overview
of the revision (Section \ref{sec:main_changes}) before answering in detail each of your comments (Section \ref{sec:detailed_answers}). Number of sections, pages and equations mentioned in the text refer to the revised version. When necessary, we refer to number of sections, pages and equations from the submitted version. In this case, they are written into brackets.

@@

\section{Main changes \label{sec:main_changes}}

The structure of the paper has been significantly modified along the revision process, in particular to take into account the referees' comments.
\begin{itemize}
	\item In the submitted version, [Section 2] was devoted to the estimation of international transport costs; specifically, their break-down in two components, additive and ad-valorem. In [Section 3], we investigated the role of additive costs in the decomposition of transport costs time trends, between structural changes and composition effects. [Section 4] was devoted to the robustness analysis relative to the results from both previous sections.
	\item In the revised version, we have substantially strengthened the robustness checks regarding the estimation of international transport costs, with the addition of detailed checks to aggregation and endogeneity. Accordingly, the previously-called [Section 2] has been split in two Sections: Section 2, where we present the data and the estimation strategy; and Section 3, where we present the the results. Section 3 now includes the robustness checks as a final sub-section. For the sake of space, the robustness analysis related to composition effects has been sent to the Appendix (Section C.3).
	\item Both referees asked us to devote more developments to the implications of additive costs (the ``Big Picture''). We do agree that this was not emphasized enough in the submitted version, and we thank the referees for their suggestions on that issue. The revised version answers this concern in two points.
	\begin{enumerate}
		\item We maintain the analysis of the transport costs time trends (previously [Section 3], now Section 4); but we improved this section's readability by leaving the technical aspects in the Appendix (Section C). As such, we hope that the main message of this Section is easier to understand.
		\item Most importantly, we now emphasize the ``Big Picture'' welfare implications of additive costs on theoretical grounds. Through the lens of the \cites{melitz} model amended to integrate additive costs, we analyze the welfare gains deriving from the reduction in international transport costs estimated in Section 3 over 1974-2019. In this regard, we shed light on the welfare variations induced by the ``hyper-globalization'' period. This also allows us to quantify the extra welfare gains attributable to reduction of additive trade costs. This analysis is performed in Section 5.

	\end{enumerate}
	\item To keep the paper (both the main text and its various appendices) within a reasonable number of pages, and stay fully transparent about our results, we have added numerous detailed tables to the Online Appendix.
\end{itemize}

@@

\textbf{Our answer:} We devoted a lot of thought to this point, which directly echoed a similar concern by the other referee. The latter writes: ``\emph{Does this observation revise our understanding of say the gains from trade? Does it shed new light on a puzzle many people are thinking about? [One] suggestion is to dig deeper into the relative rate at which additive and multiplicative transport costs have declined over time.}
''

All in all, your suggestion and the other referee's one pointed toward two possible options for the ``Big Picture'' implications of our exercise: either exploring the compositional country-product dynamics underlying of our results, or focusing on the welfare implications. Both paths were undeniably worth exploring, but could not be followed in a single paper. Therefore, we decided to focus on the second path, i.e. to  offer insights on the welfare implications of our results. In this regard, the new Section 5 ``The role of additive cost: Theoretical insights'' is devoted to a theory-based analysis of the changes to welfare gains implied by the relative variations of additive and multiplicative transport costs over our period of analysis.

Our choice to dig into the welfare implications of our results has two main motivations. Firstly, even if ``\emph{the fact that transport costs are both specific and ad-valorem is well known}'', some recent literature still debates the practical importance of additive costs - for example, \cite{Lashkaripour_JIE2020} finds evidence supporting the ad-valorem assumption for denumerable goods, and consistently finds a very small welfare effect of additive costs within a partial-equilibrium model with perfect competition. Secondly, the implications of additive costs have not been fully exhausted in \citet{Irrazabal_2015}, \cite{Hornok-et-al-RES-2015, Hornok-et-al-JIE-2015}, \cite{Alessandria-et-al-AER-2010} or \citet{sorensen2014}. \cite{Kropf-Saure-JIE-2016} estimate the size and shape of per-shipment costs based on Swiss data. \cite{Alessandria-et-al-AER-2010} and \cite{Hornok-et-al-RES-2015} point out the role of per-shipment costs in generating ``lumpiness'' in international trade transactions. \cite{Hornok-et-al-JIE-2015} focus on administrative costs incurring with every shipment (i.e., additive by nature), and draw welfare conclusions regarding the variations of these costs. We complement these various outcome by providing a long-run characterization of both additive and multiplicative component of transports costs. Based on these empirical results, we investigate the welfare consequences of the reduction in international transport costs observed over 1974-2019. In this regard, we shed light on the welfare variations induced by the ``hyper-globalization'' period, as well as the disproportionate part of additive transport costs in determining those welfare variations.\smallskip

@@

To this aim, we introduce additive costs in the canonical \citet{melitz} model. The inclusion of additive costs in a \citet{melitz} setting has already been performed in \citet{sorensen2014} and \citet{Irrazabal_2015}. However, \citet{sorensen2014} exclusively performs a theoretical analysis, without any quantitative exercise. In addition to a partial equilibrium extension of \citet{melitz}, \citet{Irrazabal_2015} do perform a quantitative simulation to assess the welfare variations induced by the reduction of additive costs (vs ad-valorem costs). For this, they rely on a calibration for transport costs based on a single-year estimation (for the year 2004), from which they depart by assuming an ad-hoc hypothetical reduction of trade costs. In contrast, our own exercise relies on a several decades of US data, allowing us to highlight the welfare alterations induced over time by the relative dynamics of additive and multiplicative costs, based on the values actually observed in the data over the period 1974-2019, in all their dimensions (additive and ad-valorem).\smallskip

More precisely, we use the estimates underlying results reported in Section 3 concerning multiplicative and additive costs, to implement several comparative statics exercises to investigate the different welfare consequences of alterations to multiplicative and additive costs. In addition, we also assess how the latter results are distorted by changes in sunk costs of exports, $f_{x}$. To that end, we adjust the share of exporting firms in the US based on \citet{BEJK-AER-03} and \citet{Lincoln_McCallum2018}. In our preferred exercise, we quantify the welfare gains deriving from the reduction in variable transport costs as documented in Section 3, relying on a combined reduction in each additive/ad-valorem component in a context of fixed export cost reduction. We compare setting this with the case where the reduction of total transport costs  is solely attributed to a decrease in ad-valorem costs.

Table 5 in Section 5 of the paper reports the results of these various comparative statics exercises for Air and Vessel transport modes. Specifically, we report the welfare effect of change in total transport costs decomposed in its two dimensions (additive and ad-valorem), both in absolute and in relative terms. We have two major insights. First, using the reduction of transport costs in vessel (air),  welfare gains are around 50\% (14\%) higher when this reduction is achieved through the estimated reduction in additive and ad-valorem costs. Second, the decrease in export sunk costs (i.e., increase in the share of exporting firms) proportionally amplifies the gains from decreasing variable costs, with again an additional premium coming from the decrease of additive costs.

Overall, these results add a substantial contribution to the paper : we are able to provide a quantitative assessment of the welfare gains induced by the decrease in both types (additive and multiplicative) of costs over a 45-year period covering the hyper-globalization moment, and to highlight the respective part of each component in the determination of these gains.
%Note also that not only the inclusion of additive costs in the underlying framework generates large welfare differences, but also that the latter are probably a lower bound of the welfare variations induced by changes in additive \emph{trade} costs, larger than the sole transport costs.

@@

\begin{equation}
p_{ikt}=\tau_{it}\widetilde{p}_{ikt}+ \tau_{kt}\widetilde{p}_{ikt} + t_{it} + t_{kt} + \epsilon_{ikt}   \label{eq:ref2_basis}
\end{equation}

\textit{I do not see why the authors need the complicated non-linear transformations to do what they aim
for. Estimating Equation (\ref{eq:ref2}) should be relatively easy, for one it is linear, but it would also not require the
inclusion of any country-sector fixed effects.}

\begin{equation}
p_{ikt}= \sum_i \sum_t \alpha_{it}^\tau \mathbbm{1}_{it}\widetilde{p}_{ikt} +  \sum_k \sum_t \alpha_{kt}^\tau \mathbbm{1}_{kt}\widetilde{p}_{ikt} + \sum_i \sum_t \alpha_{it}^t \mathbbm{1}_{it} + \sum_k \sum_t \alpha_{it}^t\mathbbm{1}_{kt} \label{eq:ref2}
\end{equation}

\textbf{Our answer:} As highlighted by the referee, our estimated equation imposes to use non-linear estimation methods, such as Non-Linear Least Squares. We agree that resorting on a linear form as the one suggested by the referee would substantially alleviate the computational burden. However, it would have some important drawbacks.

First, it can be noticed that the equation suggested by the referee does not stand in accordance with the assumption we borrow from \cite{Irrazabal_2015}, that ad-valorem costs is decomposed in its two country/sector dimensions multiplicatively (i.e. approximating $\tau_{is(k)}$ by the product $\tau_i\times \tau_{s(k)}$).

@@

However, even with another formulation, such as the equations (\ref{eq:ref2_basis}) and (\ref{eq:ref2}) suggested by the referee, we would still be constrained to resort to non-linear estimators. This is due to the restrictions imposed \textit{ex-ante} on parameters, i.e. $\tau \geq 1$ and $t\geq 0$, the latter meaning simply we constrain both types of transport costs to be non-negative, as by construction we cannot have $p_{ikt} < \widetilde{p}_{ikt}$. Without these restrictions, standard linear, least squares estimates deliver aberrant values with mediocre quality-of-fit. Taking into account $p_{ikt} < \widetilde{p}_{ikt}$ also implies that the error term should be always positive, which we ensure by specifying the error term such that:

\begin{equation*}
\frac{p_{ik}}{\widetilde{p}_{ik}}-1 =\left(\tau_{i}\times \tau_{k} -1+\frac{t_{i} + t_{k}}{\widetilde{p}_{ik}} \right)\times \exp(\epsilon_{ik})
\end{equation*}
\noindent where $\epsilon_{ik}$ follows a normal law centered on 0.

This specification obviously requires a non-linear estimation. We did our best to make the point clearer in the revised version (see section 2.2, more specifically p. 8). We also devote more time to the robustness of the empirical specification. On top of the robustness to the separability assumption (already in the previously submitted version), we also assess the robustness to endogeneity and the level of aggregation (Sections 3.3.2 and 3.3.3). We hope that this new version will convince you that our estimation strategy is both relevant and robust.
